Figures

### 2020-03-18 figures/07_model-selection.Rmd
adjust figure labels

label_key <- data.frame(labels = c("Aggregate", "Granular", "Other"), 
                        x = c(0, 0, 0), 
                        y = c(0.62, 0.49, 0.37), 
                        stringsAsFactors = FALSE)
gg_labels <- ggplot() + geom_text(data = label_key, 
                                        aes(x = x, y = y, label = labels), angle = 90) +
    expand_limits(y = c(0.3, 0.7)) +
    theme_void()
gg_tp <- cowplot::plot_grid(gg_labels, 
                   gg_tp, rel_widths = c(0.3, 1))

>>>>

label_key <- data.frame(labels = c("Aggregate", "Granular", "Other"), 
                        x = c(0, 0, 0), 
                        y = c(0.665, 0.54, 0.37), 
                        stringsAsFactors = FALSE)
gg_labels <- ggplot() + geom_text(data = label_key, 
                                        aes(x = x, y = y, label = labels), angle = 90) +
    expand_limits(y = c(0.3, 0.7)) +
    theme_void()
gg_tp <- cowplot::plot_grid(gg_labels, 
                   gg_tp, rel_widths = c(0.3, 1))
